Heatmaps of pleiotropy test statistics

### 2019-07-23 analysis/paper/figures.Rmd
updated figures

>>>>

```{r scatter-2}
p <- pleio_mixed_list %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  inner_join(med_tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  dplyr::select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id) %>%
  ggplot() + geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, xlab = "Pleiotropy LOD", ylab = "Mediation LOD difference", colour = local_symbol, nonlocal = nonlocal_symbol), size = 0.05) + theme(legend.position = "none")
fnsvg <- paste0("Chr", hot_chr, "_scatter.svg")
fnpdf <- paste0("Chr", hot_chr, "_scatter.pdf")
ggsave(plot = p, filename = file.path("../figures", fnsvg))
ggsave(plot = p, filename = file.path("../figures", fnpdf))
```
